Palomar 5 Gaps

### 2024-09-30 paper/main.tex
first pass at the morphology

 \subsection*{Gap Morphology}

>>>>

 \subsection*{Gap Morphology}
  We study the structure of the streams that have been impact by the globular clusters. The gallery of gaps is shown in the appendix, which includes the results from all of the simulations we considered in this experiment.

  In general, how did the passage of these globular clusters effect the stream? well. A lot of this has been studied quite well and presented in Sanders et al 2016. They even consdiered different types of impactors. I.e. impactors that had different density profiles. They compared Hernquist, Plummer, NFW, and a truncated NFW. There are some minor differences between the impactors however, the conclusion is still the same. Impacts from small and dense perturbers such as globular clusters only effect the stream locally.

  Our results are consistent with those shown previously. Perturber crossings only perturb the stream locally. Global characterisitcs of the stream do not change. For instance, the stream is not warmer of thicker. Other types of interactions have been demonstrated to do this. For example THIS AUTHOR showed that XXX and do YYY. As laid out in Erkal et al 2015, perturbers pull particles from the sides towards the impact point. These particles eventually move beyond the impact point and leave an under dense center and then pile up on the sides leaving an overdensity on the shoulders.

  Interestingly, most of our gaps occur for the leading tail. 8 on the trailing tail. 21 excluding NGC~2808 are on the leading tail. We have to exclude NGC~2808 because the simulations are clearly correlated with one another, so trials are not independent. So is 8/29 consistent with a fair coin toss? In anycase, we argue this may be a coincidence since being hit should only depend on the size and location of the stream. The main difference between the tails is a $\approx$ 300-400 pc offset in $r$, yet this is negligible.

  All of the gaps are oblique in tail coordinates. This is an artifact of using tail coordinates and arrises because we project the star-particles onto the nearest point of the orbit. (this is really difficult to explain with words and super simple with a picture. The picture being that we have three evenly spaced parallel lines that are close together. Then, a third point that is far away.  )

  Do our gaps grow linearly in time? what about this square root stuff?

  Lastly, since the streams have width, there are some instances where the stream is not significantly impact across this width. For instance, the gaps from NGC~5284 in Sampling 019 and NGC~6333 in Sampling 033 are more akin to bites than gaps.
